---
title: "Olive Traning: Data Scince"
date: "Jan-April 2023"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

* web Scraping in R can be done in 3 different way: 
  + by Target the HTML Tags via G-Extension 
  + by Target the JSON in Developers Mode Network
  + by Fetching the API and using CURL code 

## Targetting the Html tags is more functional and manual way, for colloctiong the data's from any server 
  
### 1- for the first step we have target the base page and collect all the links, that has data 

```{r echo=TRUE,warning=FALSE, message= FALSE}
# BasePage: https://www.motorcycle.com/specs/kawasaki.html

library(rvest)
library(data.table)
library(kableExtra)
library(dplyr)

# 1 get all the link. save it
vector_of_all_links <- c()

# we target from page1-3 for reload and work faster
for (pageNum in 1:3) {
    
  url <- paste0("https://www.motorcycle.com/specs/kawasaki.html?page_num=", pageNum)
  
  t <- read_html(url)
  
  relative_link <- t %>% html_nodes('.flex-one a') %>% html_attr('href')
  relative_link <- gsub('#UserReviews','',relative_link)
  
  vector_of_all_links <- append( vector_of_all_links, relative_link)
}

```

### 2- createing a function that takes one link, and return with a list, which contain all the data of the motor.
  
```{r echo=TRUE,warning=FALSE, message= FALSE}

get_motors_details <- function(url) {
  
  motor_data <- read_html(paste0('https://www.motorcycle.com',url))
  
  motor_details <- list()
  
  motor_details[["Title"]] <- motor_data %>% html_nodes('.sl-post-title') %>% html_text()
  key <- motor_data %>% html_nodes('.spec-key.bold') %>% html_text() %>% trimws()
  value <- motor_data %>% html_nodes('.vs-specs-table-row .spec-value') %>% html_text() %>% trimws()
  
  if(length(key)==length(value)){
    for (i in 1:length(key)) {
      motor_details[[key[i]]] <- value[i]
    }
  }
    return(motor_details)
}
```

###  looping the function to all links, and saveing as new data (data.frame)

```{r echo=TRUE, message=FALSE, warning=FALSE}

read_all_links <- lapply(vector_of_all_links, get_motors_details)

# convert to data.frame
motors_df <- rbindlist(read_all_links, fill = T)

```

### Saving our data as .RDS file for avoiding the 404/402 Error from Server 

```{r echo=TRUE,warning=FALSE, message= FALSE}

# Saving our data as .RDS file for avoiding the 404/402 Error from Server 
saveRDS(motors_df,'motors_data.rds')

```

###  View of our data in .RDS file as table

```{r echo=TRUE,warning=FALSE, message= FALSE}
library(kableExtra)

table <- readRDS('/Users/JM/greenFox/CEU-Traning/R/week_11/motors_data.rds' )

table %>% 
  kable(booktabs = TRUE) %>%
  kable_paper("hover",font_size = 9) %>% 
  row_spec(0, bold = T, color = 'white',background = "black") %>% 
  column_spec(1, bold = TRUE, border_right = TRUE, color = "black", background = "lightgrey") %>% 
  scroll_box(width = "100%", height = "650px")

```

# ggplot()
### Clean Data: Selection our Target columns from data may help us to have better visulation 

```{r echo=TRUE,warning=FALSE, message= FALSE}
library(rvest)
library(dplyr)
#df <- readRDS('/Users/JM/greenFox/CEU-Traning/R/week_11/motors_data.rds' )
df <- motors_df

names(df)[11]<-"Name"
names(df)[2]<-"Type"
names(df)[3]<-"Price"
names(df)[5]<-"Warranty"
Year <- df$Year

df$Price<-gsub("\\$","",df$Price) # delete the $ sign
df$Price<-gsub("\\,","",df$Price) # delete the , sign 
df$Price<- as.numeric(as.character(df$Price)) # convert the string to number

View(df)

```


### First graph show you the Name and Price of each Kawasaki model


```{r echo=TRUE,warning=FALSE, message= FALSE}

library(ggplot2)

ggplot(df, aes(x=Name, y=Price))+  
  geom_col(color="grey", fill="black")+
  theme_bw()+
  coord_flip()+
  theme(axis.text.x = element_text(angle =60, vjust=0.5,hjust=0.5))+
  labs(x="Name",y="Price", title = "Kawasaki Details")


```

```{r echo=TRUE,warning=FALSE, message= FALSE}

ggplot(df, aes(Price, fill =Type, colour = Type)) +
  geom_density(alpha = 0.2) +
  xlim(1000, 30000)


```


### BoxPlot chart to Visual the Kawasaki Price in Type

```{r echo=TRUE,warning=FALSE, message= FALSE}

df_1 <- df %>% 
  select(Name,Price,Type) %>% 
  group_by(Type) %>% 
  arrange(Price) %>% 
  head(20)

  ggplot(df_1, aes(Type, Price))+
  geom_boxplot(aes(color=Type))


```

### With Bar_Plot chart we can have select models warranty/price

```{r echo=TRUE,warning=FALSE, message= FALSE}


df_2 <- df %>% 
  select(Name,Price,Type, Year, Warranty) %>% 
  group_by(Type) %>% 
  arrange(Price)
  
number_of_bar <- nrow(df_2)
angle <-  90 - 360 * (df_2$Price-0.5) /number_of_bar # ? we should have numaric value for price to have right chart


df_2$hjust<-ifelse( angle < -90, 1, 0)


df_2$angle<-ifelse(angle < -90, angle+180, angle)

# -----------------------------
ggplot(df_2, aes(x=Name, y=Price)) +  
  geom_bar(stat="identity", fill=alpha("blue", 0.3)) +
  ylim(-28000,35000) +
theme_minimal() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
   # plot.margin = unit(rep(-2,4), "cm")     # This remove unnecessary margin around plot
  ) +
  coord_polar(start = 0)+
  geom_text(data=df_2, aes(x=Name, y=Price, label=Name, hjust=hjust), color="black", fontface="bold",alpha=0.4, size=2, angle= df_2$angle, inherit.aes = FALSE ) 

```


### Model Price in Animation chart 

```{r echo=TRUE,warning=FALSE, message= FALSE}
library(ggplot2)
library(dplyr)
library(gganimate)
library(hrbrthemes)
library(viridis)
library(gifski)


df_3 <- df %>% 
  select(Name,Price,Type) %>% 
  group_by(Type) %>% 
  arrange(-Price) %>% 
  head(50)

  ggplot( aes(x=Type, y=Price, group=Type, color=Type), data = df_3)+
  geom_line()+
  geom_point()+
  #transition_states(x) +
  scale_color_viridis(discrete = TRUE) +
  ggtitle("Price of the Kawasaki models") +
  theme_ipsum() +
  coord_flip()+
  theme(axis.text.x = element_text(angle =60, vjust=0.5,hjust=0.5))

  # Render the animation
  #anim <- animate(df_3, nframes = 10)
  
  # Save the animation
  #anim_save("animation.gif", anim, renderer = gifski_renderer())
  
  
```


